
%% If you need to pass whatever options to xcolor
\PassOptionsToPackage{dvipsnames}{xcolor}

%% If you are using \orcid or academicons
%% icons, make sure you have the academicons
%% option here, and compile with XeLaTeX
%% or LuaLaTeX.
% \documentclass[10pt,a4paper,academicons]{altacv}

\documentclass[10pt,a4paper,ragged2e]{maltacv}

%% AltaCV uses the fontawesome and academicon fonts
%% and packages.
%% See texdoc.net/pkg/fontawecome and http://texdoc.net/pkg/academicons for full list of symbols. You MUST compile with XeLaTeX or LuaLaTeX if you want to use academicons.

% Change the font if you want to
% If using pdflatex:
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
% \usepackage[default]{lato}
\usepackage{tgheros}
\renewcommand*\familydefault{\sfdefault} %% Only if the base font of the document is to be sans serif

\usepackage{setspace}
\usepackage{mathpazo}
\usepackage{textcomp}
\usepackage{multicol}

% Color schemes:
% raisinblack_flame
% darkpurple_princetonorange
% blue_claret
% eerieblack_eggplant
% outerspace_forestgreen   
% raisinblack_midnightgreen
% teal_brown
% indigo
% blue
% violet
% you can set your custom colors with:
% \definecolor{AccentBody}{HTML}{002642}
% \definecolor{Primary}{HTML}{840032}
% \colorlet{primary}{Primary}
% \colorlet{accent_body}{AccentBody}

% this is my favourite but change it as you like
\setcolorscheme{eerieblack_eggplant}
\setlength\multicolsep{0pt}
% Change the bullets for itemize and rating marker
% for \cvskill if you want to
\renewcommand{\itemmarker}{{\small\textbullet}}

%% sample.bib contains your publications
%% NOT SUPPORTED YET
% \addbibresource{sample.bib}

\name{Tarun Bansal}
\firstname{Tarun}
\familyname{Bansal}

\begin{document}
\tagline{Software Engineer}
\personalinfo{%
  % Not all of these are required!
  % You can add your own with \printinfo{symbol}{detail}
  \email{officialtarunbansal@gmail.com}
  % \birthday{25\textsuperscript{th} Dec 0}
  % \homepage{www.homepage.com/}
  % \twitter{@twitterhandle}
  \linkedin{officialtarun}
  \github{tarun4all}
  \location{New Delhi, India}
  \phone{+91 9650849625}
  \graduation{BCA}
}

\bio{3+ years of experience solving engineering problems. 1+ years of experience writing Go code in production. 3+ years of experience writing JavaScript code. Deft at reverse engineering. Adept at writing testable, modular and simple code.}

\makecvheader

\cvsection{Experience}

\cvexperience{Software Engineer}{Sourcefuse Technologies}{Jan 2021 - Present}{New Delhi, DL, India}{Golang, JavaScript, React, Redux, NodeJS}
\begin{itemize}
  \item Implemented pipeline for Sonarqube scan, ES Lint check for build and TODO List based on comments .
  \item Worked on Scalable component for Rakuten A2P.  
  \item Created common theme components for resume in All Rakuten Products and to Handle material UI version upgrade
  \item Worked on Test cases based on User Role.
  \item Worked on TDD for new Features and approach.
  \item Worked on Golang Service for Analytics in
  \href{https://privatewealthsystems.com/}{PWS}
\end{itemize}

\cvexperience{Full Stack Developer}{Codalien Technologies Pvt. Ltd.}{July 2019 -- Dec 2020}{New Delhi, DL, India}{Golang, JavaScript, ReactJS, NodeJS, Express, Redux, MongoDB, GraphQL}
\begin{itemize}
  % \item Worked on various web and mobile applications powered by latest frontend technologies.
%   \item Developed both frontend (web and mobile) applications as well as backend services powered by latest web technologies and frameworks.
  \item Developed GoLang Module to parse questionnaire at \href{https://yubihealth.com/}{Yubi Health}
  \item Developed web app with Test case for Decision maker that powers questionnaire for Mental Health \href{https://yubihealth.com/}{Yubi Health's}
  \item Created various dynamic components with reusability in mind (such as a reusable Table Group with support for server-side pagination, filtering and sorting) for data/info centric applications
  \item Developed and integrated various REST API and GraphQL services in both backend and frontend side.
  \item Developed payment integration(Stripe), calendar implementation, location services and authentication at Yubi Health
  \item Assisted and lead development of admin panels and content management systems powered by KeystoneJS (Node, MongoDB, React).
\end{itemize}

\divider

\cvexperience{Software Engineer}{Notifyvisitors Technologies AKA TagnPin Technologies}{Jan 2019 - June 2019}{New Delhi, DL, India}{ReactJS, Redux, EC2, S3, Linux}
\begin{itemize}
  % \item Worked independently as well as assisted senior developers in various coding and testing functions. 
  \item Worked on Javscript SDK and lerna build to Integrate on other web app for different products. 
  \item Developed Node API's for analytic and stats for Heat-map and Chat-bot. 
  \item Build reusable component with React JS for dashboard.
\end{itemize}

\divider
\medskip

% \cvsection{Education}
% \medskip
% \begin{multicols}{3}
%   \cvuniversity{B.Tech. (CSE)}{Inderprastha Engg. College (AKTU)}{2017}{Ghaziabad, UP}% last param is location
%   % this helps if columns are not the same
%   \vfill\null
%   \columnbreak

%   \cvuniversity{XIIth (CBSE)}{Tagore Sr. Sec. School}{ 2012 }{Mayapuri, Delhi}{}
%   \vfill\null
%   \columnbreak

%   \cvuniversity{Xth (CBSE)}{N.C. Jindal Public School}{ 2010 }{Punjabi Bagh, Delhi}{}
%   \vfill\null
%   \columnbreak
% \end{multicols}
% \medskip


\cvsection{Technical Skills}
\medskip
  % \begin{multicols}{5} % adjust #cols as needed
    \cvtag{Docker}{}
    \cvtag{JavaScript}{}
    \cvtag{TypeScript}{}
    \cvtag{ReactJS}{}
    \cvtag{Golang}{}
    \cvtag{React Native}{}
    \cvtag{Redux}{}
    \cvtag{NodeJS}{}
    \cvtag{Express}{}
    \cvtag{GraphQL}{}
    \cvtag{MongoDB}{}
    \cvtag{Redis}{}
    \cvtag{Linux}{}
    \cvtag{Unix}{}
    \cvtag{Serverless}{}
    \cvtag{AWS}{}
    \cvtag{Git}{}
    \cvtag{MySQL}{}
    \cvtag{Firebase}{}
    \cvtag{Kubernetes}{}
    \cvtag{react-query}{}
    \cvtag{Axios}{}
    \cvtag{Postman}{}
    \cvtag{SonarQube}{}
    \cvtag{Jira}{}
    \cvtag{Agile}{}
    \cvtag{Confluence}{}
    \cvtag{Material UI}{}
    \cvtag{Ant Design}{}
    \cvtag{Cobra}{}
    \cvtag{Jest}{}
    \cvtag{Enzyme}{}
    \cvtag{Testify}{}
    \cvtag{Webpack}{}
  % \end{multicols}
\medskip
\divider

\cvsection{Interests}
\begin{multicols}{3} % adjust cols as needed
  \cvlistitem{Music}{Cigarettes after sex, The Strumbellas}
  \cvlistitem{Alexa Automation}{Zoom Integration, Login/Logout, Github Task List}
  \cvlistitem{Video Games}{CS:GO, GTA, Watchdogs}
\end{multicols}

% try to keep it on one page only !
\end{document}
